Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-08 hotstorage13/abs.tex
evaluation changes
ispell

\begin{abstract}
%Virtualization has became the engine behind many cloud computing platforms.
In a virtualized cloud cluster, frequent  snapshot backup of virtual disks improves
hosting  reliability; howver, it  takes significant 
memory and CPU resource to perform data duplication in order to remove
excessive redudancy among snapsots.
This paper presents a low-cost clustered deduplication soluton scalable for handling a large number 
of virtual machines.  The key idea is to seperate duplicate detection from 
the actual storage data backup instead of using inline deduplication, and partition
global index and  detection requests among machines using  fingerprint values.
Then each machine conducts duplicate detection partiton by partition indepdently with a minimal memory usage.
%in parallel among all machines and  each machine full duplication detection is 
Another optimization is to allocate and control
buffer space for exchanging  detection messages and duplicate summary among machines.
%The memory requirement and disk usage for the proposed solution is very small while the overall thoughput
%and backup process timing is not compromised. 
Our experiments show that  the proposed scheme 
uses a very small amount of system resources while accomplishing a satisfactory backup throughput
in a large cloud setting.
%which only reqiires a very small amount of memory and CPU resource.  
%Experimental results  show the proposed scheme  can achieve high deduplication ratio while using
%a  small  amount of cloud resources.

>>>>

\begin{abstract}
%Virtualization has became the engine behind many cloud computing platforms.
In a virtualized cloud cluster, frequent  snapshot backup of virtual disks improves
hosting  reliability; however, it  takes significant 
memory and CPU resource to perform data duplication in order to remove
excessive redundancy among snapshots.
This paper presents a low-cost clustered deduplication solution scalable for handling a large number 
of virtual machines.  The key idea is to separate duplicate detection from 
the actual storage data backup instead of using inline deduplication, and partition
global index and  detection requests among machines using  fingerprint values.
Then each machine conducts duplicate pre-detection partition by partition independently with a minimal memory usage.
%in parallel among all machines and  each machine full duplication detection is 
Another optimization is to allocate and control
buffer space for exchanging  detection messages and duplicate summary among machines.
%The memory requirement and disk usage for the proposed solution is very small while the overall thoughput
%and backup process timing is not compromised. 
Our experiments show that  the proposed scheme 
uses a very small amount of system resources while delivering a satisfactory backup throughput.
%in a large cloud setting.
%which only reqiires a very small amount of memory and CPU resource.  
%Experimental results  show the proposed scheme  can achieve high deduplication ratio while using
%a  small  amount of cloud resources.

### 2013-03-08 hotstorage13/arch.tex
ispell

\item {\bf Seperation of duplicate detection and data backup.}
%Request accumulation and partition-based deduplication.}
The second level duplicate detection requires a global comparison of 
content fingerprints of stored chunks with the new chunks scanned during 
the backup process. Bloom filters and caching allows some of content 
fingerprints to be stored on the cheap disks~\cite{bottleneck08}. Such an optimization is good 
for inline deduplication where chunks scanned need to be determined to be duplicate or not instantly without 
waiting while  it memory consumption is still significant in competing with stand virtual 
machine activities.  Our idea is to perform duplicate detection first before actual data backup.
That requres a pre-scanning of  data  blocks of VM images and after that, real backup  for those nonduplicates
is conducted. That does incur an extra  round of I/O reading for nonduplicate blocks while avoiding inline 
deduplication and leading to a much smaller resource requirement. 
During duplicate detection phase, detection requests can be accmnulated on the disk 
for a period time  in a  partitioned manner.  Aggregated duplicate requests can be processed partition by partition. 
%We also accumulate the delete requests and perform them partition by partitions. 
Since each partition corresponds to a small portion of global content index, the cost to 
process requests within a partition is significant smaller than process all the requests globally.

\item {\bf Buffered data redistrubution in parallel duplicate detection}.  
We let {\em global index} be the meta data containing the fingerprint values of all unique blocks
in the entire cluster and  the reference pointers which lead to the actual location of raw data.
A dupliate detection request for a content block needs to be compared with the global index to determine if this
block is nonduplicate. If it is a duplicate, return the correspinding reference pointer.
We conduct parallel processing of detection requests in all machines in a cloud cluster.
A logical way to distribute detection requests is to parititon based on the content  hashing of data blocks
and the global index can also be partitioned accordingly in a  disjointed manner.
Initial data follows the VM distribution among machines and the detected results 
represented as  duplicate summary need to be collected following VM distribution. 
Therefore, there are two all-to-all data remapping operations involved.
One is to map detection requests from VM-based requests to the fignerprint based distribution.  
One is to map dupliate summary from fingerprint-based requests to the VM based distribution.  
The redistribued data needs to be accumulated on the disk to minimize the use of memory.
To minimize the cost of disk seek, outgoing or incoming data exchange messages need to be buffered to bundle small messages.
Given there are $p\times q$ partitions where $p$ is the number of machines and $q$ is the number of fingerprint-based partitions
at each machine, the number of buffers is big and space per each buffer  is small given the memory constraint.
Then there will be a large number of storage  IO operations involved, suffering the huge seek overhead.
We have designed an effient data exchange and disk data buffering  scheme to address this.

@@

We assume a flat architecture in which  all $p$ machines that host VMs in a cluster can 
be used in parallel for deduplication. 
The nonduplicated snapshot blocks are stored either in a distribed file system built on
this cluster  or in another  external storage system. 
We assume that  a small amount of local disk space and memory on each machine can be used 
to store global index and request accmulation.
%Our design is to minimize the usage of local memory and storage on each machine.

@@

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{snapshopdata.pdf}
\caption{ Metadata strucrure of a VM snapshot.}
\label{fig:snapshot}
\end{figure}

@@

Segment metadata (called segment recipe) records its  content block hashes and data pointers. 
The snapshot recipe contains a list of segments and other meta data information.
If a segment is not changed from one snapshot to another, indicated by a dirty bit embedded in the virtual disk driver, 
its content blocks are not changed as well, thus its segment recipe contains a reference pointer to an earlier segement.
If a block is dupliate to another block in the system,  the block recipe contains a reference pointer to an earlier block.

@@

The data flow of our partition-based  dupliate detectionis depicted in
Figure~\ref{fig:flow}. 
%let $v$ be the total number of virtual machines hosted in  a cluster,  
%we divide the backup into $k$  iterations. 
\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{steps.pdf}
\caption{ Processing steps of dupliate detection.}
\label{fig:flow}
\end{figure}

\begin{itemize}
\item
The first step is that each machine independently reads  
%$v/k$  
virtual machine images that need a backup
and forms duplicate  detection requests. For those segments that have been modified since last backup indicated by 
dirty bits,  the system divides  each segment into a sequence of chunk blocks,  computes the meta 
information such as chunk fingerprints,  sends the metadata of a chunk block, and accumulate  into 
a partition bucket on the temporary disk storage. 
The partition mapping is using a hash function applied to the content fingerprint. 
Assuming all machines have a  homogenous resource configuration, each machine is evently  assigend with
$q$ partitons of content hash and accumulates corresponding requests on the disk. 
There are two options to assign buffers in each machine to buffer requests for each partition.
1) Each machine has  $p\times q$ send buffers corresponding to $p\times q$ partitions in the cluster
since any content block in a VM image of this machine can be sent to any of these partitions.
2) Each machine has $p$ receive buffers correspond to $p$ machines in the cluster and $q$ receive 
buffers to temporarly accmulate messages from other machines, and then output each buffer to the local disk
when it becomes full.  Option 2 is much more efficient than Option 1 because $p+q$ is much smaller than
$p\times q$, as a result each buffer has a bigger size to accmulate data and results in 
much less disk seek overhead.

%We assume that the startup cost for network message sending is  much more less (e.g. an order of magnitude
%less) than from one machine to another 
%disk storage startup cost such as seek is much mu
%Note that we only accumulate requests with their meta data information.
\item
The second step is to perform duplicate detection for  all requests accumulated in the partitions.  
The system maintains the index of all chunk fingerprints divided in the buckets. We load the global index partition 
and accumulated correspnding requests, and compare them to  identify the duplicated blocks.  
Then we unloand them, load the global index and accumulated requests for another partition. 
This process is repeated until all buckets are processed.

As chunk blocks are detected as duplicates, the meta information on duplicates is 
remapped from fingerprinter-based distribution  to VM-based distribution. In this way, duplicate information 
for segments of each VM is collected in one place, which will be used in next step. 
In the sending side, each machine scans idenitified duplicates for one target machine,
and then scans for another machine. In this way, it sends dummary summary to the corresponding machines one by one
to minimize the startup cost for sending a message.
In the receiving side, 
%All-to-all machines data exchange is conducted  so that  
each machine allocates $q$ receive buffers corresponding to
$q$ local partitions, to hold received messages from other machines.  
When a receive buffer for a VM is  full, the data is written to the local disk storage. 
%These substeps are repeated as the stream of data is exchanged when each machine compares through all $q$ partitions.

\item The third step is to read  nonduplicate blocks from each VM and output to the final backup 
storage. Additionally, the global index on each machine is updated with the meta data of new chunk blocks added.
In this process, if a segment is not dirty, we only need to output the segment meta data 
such as reference pointers to the original segments previously saved in the backup.  
If a segment is dirty,  we use the duplicate summary information from Step 2 for internal 
duplicate blocks of this dirty segment and output the remaining non-duplicate blocks to the backup storage.
\end{itemize}

@@

%1) $p$ send buffers. images, sends the fingerprint of a dirty block to a machine that is responsible for this fingerprint.
%2) Buffer requests gathered from other machines and divide those requests into $q$ buckets. Once a buffer for each bucket is full, output to the disk storage.
\item 
For Step 2,  the allocated memory serves 2 purposes. 1) Space for hosting a partition of global index and 
the corresponding partition of  deduplication requests. 2) Buffer space for $q$ receive buffers.
%%accumulating duplicate summary for each targeted VM.   Once  each machine processes a bucket of  duplicate detection requests, 
The duplicate summary sent other machines and accmumated for each VM contains
the block ID and  the reference pointer.   
%For each machine which hosts $v$  VMs, and will receive messages from many other machines, 
%the system needs to allocate buffer space for each VM ot accumulate the duplicate summary records. 
%When a buffer for a VM is full, the result is written to the disk.

\item For Step 3 to  perform the real backup for each VM, 
memory is used to hold the meta information summary of all duplicate blocks obtained  from Step 2. 
Another memory usage is to fetch a sequence of blocks from a virtual machines (most of them are nonduplicate) 
and write them to the  backup storage.

@@

{\bf Snapshot deleteion.} Each virtual machine will keep at most $x$ snapshots of VM images and thus
expired snapshots will be deleted unless its owern explicitly asks for its retention. 
A block or the entire segment can be deleted if its reference counter is zero.
%As we discussed in Section~\ref{sect:data}, the reference counter is kept in the global index, partitioned among machines. 
We perioidcally read all receipts of active 
snapsots and compute the counter of all blocks while still following the fingerprint-based partitioning.
That is based on the idea of mark-and-sweep~\cite{MarkSweep} while 
we deal such snapshot deletion in three partition-based steps similar to the VM snapshot backup.
Step 1 is to read  the meta data of snapshots such as segment and block
recipes and  accumate  reference count requests in different machines  in the fingerprint based distribution.
The second step  is to count references within each partition and detect those records with zero 
reference. The third step is that every VM gathers the confirmed deletion requests for its cotent and sends them
to the backup storage.
The archival data repository may log these deletion requests,  and will periodically perform a compaction operation when 
its deletion log is too big. 
%Due to the paper constraint, we will not discuss the deletion operations in details.

>>>>

\item {\bf Separation of duplicate detection and data backup.}
%Request accumulation and partition-based deduplication.}
The second level duplicate detection requires a global comparison of 
content fingerprints of stored chunks with the new chunks scanned during 
the backup process. Bloom filters and caching allows some of content 
fingerprints to be stored on the cheap disks~\cite{bottleneck08}. Such an optimization is good 
for inline deduplication where chunks scanned need to be determined to be duplicate or not instantly without 
waiting while  it memory consumption is still significant in competing with stand virtual 
machine activities.  Our idea is to perform duplicate detection first before actual data backup.
That requires a pre-scanning of  data  blocks of VM images and after that, real backup  for those non-duplicates
is conducted. That does incur an extra  round of I/O reading for non-duplicate blocks while avoiding inline 
deduplication and leading to a much smaller resource requirement. 
During duplicate detection phase, detection requests can be accumulated on the disk 
for a period time  in a  partitioned manner.  Aggregated duplicate requests can be processed partition by partition. 
%We also accumulate the delete requests and perform them partition by partitions. 
Since each partition corresponds to a small portion of global content index, the cost to 
process requests within a partition is significant smaller than process all the requests globally.

\item {\bf Buffered data redistribution in parallel duplicate detection}.  
We let {\em global index} be the meta data containing the fingerprint values of all unique blocks
in the entire cluster and  the reference pointers which lead to the actual location of raw data.
A duplicate detection request for a content block needs to be compared with the global index to determine if this
block is non-duplicate. If it is a duplicate, return the corresponding reference pointer.
We conduct parallel processing of detection requests in all machines in a cloud cluster.
A logical way to distribute detection requests is to partition based on the content  hashing of data blocks
and the global index can also be partitioned accordingly in a  disjointed manner.
Initial data follows the VM distribution among machines and the detected results 
represented as  duplicate summary need to be collected following VM distribution. 
Therefore, there are two all-to-all data remapping operations involved.
One is to map detection requests from VM-based requests to the fingerprint based distribution.  
One is to map duplicate summary from fingerprint-based requests to the VM based distribution.  
The redistributed data needs to be accumulated on the disk to minimize the use of memory.
To minimize the cost of disk seek, outgoing or incoming data exchange messages need to be buffered to bundle small messages.
Given there are $p\times q$ partitions where $p$ is the number of machines and $q$ is the number of fingerprint-based partitions
at each machine, the number of buffers is big and space per each buffer  is small given the memory constraint.
Then there will be a large number of storage  IO operations involved, suffering the huge seek overhead.
We have designed an efficient data exchange and disk data buffering  scheme to address this.

@@

We assume a flat architecture in which  all $p$ machines that host VMs in a cluster can 
be used in parallel for deduplication. 
The non-duplicate snapshot blocks are stored either in a distributed file system built on
this cluster  or in another  external storage system. 
We assume that  a small amount of local disk space and memory on each machine can be used 
to store global index and request accumulation.
%Our design is to minimize the usage of local memory and storage on each machine.

@@

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{snapshopdata.pdf}
\caption{ Metadata structure of a VM snapshot.}
\label{fig:snapshot}
\end{figure}

@@

Segment metadata (called segment recipe) records its  content block hashes and data pointers. 
The snapshot recipe contains a list of segments and other meta data information.
If a segment is not changed from one snapshot to another, indicated by a dirty bit embedded in the virtual disk driver, 
its content blocks are not changed as well, thus its segment recipe contains a reference pointer to an earlier segment.
If a block is duplicate to another block in the system,  the block recipe contains a reference pointer to an earlier block.

@@

The data flow of our partition-based  duplicate detection is depicted in
Figure~\ref{fig:flow}. 
%let $v$ be the total number of virtual machines hosted in  a cluster,  
%we divide the backup into $k$  iterations. 
\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{steps.pdf}
\caption{ Processing steps of duplicate detection.}
\label{fig:flow}
\end{figure}

\begin{itemize}
\item
The first step is that each machine independently reads  
%$v/k$  
virtual machine images that need a backup
and forms duplicate  detection requests. For those segments that have been modified since last backup indicated by 
dirty bits,  the system divides  each segment into a sequence of chunk blocks,  computes the meta 
information such as chunk fingerprints,  sends the metadata of a chunk block, and accumulate  into 
a partition bucket on the temporary disk storage. 
The partition mapping is using a hash function applied to the content fingerprint. 
Assuming all machines have a  homogeneous resource configuration, each machine is evenly  assigned with
$q$ parititons of content hash and accumulates corresponding requests on the disk. 
There are two options to assign buffers in each machine to buffer requests for each partition.
1) Each machine has  $p\times q$ send buffers corresponding to $p\times q$ partitions in the cluster
since any content block in a VM image of this machine can be sent to any of these partitions.
2) Each machine has $p$ receive buffers correspond to $p$ machines in the cluster and $q$ receive 
buffers to temporarily accumulate messages from other machines, and then output each buffer to the local disk
when it becomes full.  Option 2 is much more efficient than Option 1 because $p+q$ is much smaller than
$p\times q$, as a result each buffer has a bigger size to accumulate data and results in 
much less disk seek overhead.

%We assume that the startup cost for network message sending is  much more less (e.g. an order of magnitude
%less) than from one machine to another 
%disk storage startup cost such as seek is much mu
%Note that we only accumulate requests with their meta data information.
\item
The second step is to perform duplicate detection for  all requests accumulated in the partitions.  
The system maintains the index of all chunk fingerprints divided in the buckets. We load the global index partition 
and accumulated corresponding requests, and compare them to  identify the duplicated blocks.  
Then we unload them, load the global index and accumulated requests for another partition. 
This process is repeated until all buckets are processed.

As chunk blocks are detected as duplicates, the meta information on duplicates is 
remapped from fingerprint-based distribution  to VM-based distribution. In this way, duplicate information 
for segments of each VM is collected in one place, which will be used in next step. 
In the sending side, each machine scans identified duplicates for one target machine,
and then scans for another machine. In this way, it sends duplicate summary to the corresponding machines one by one
to minimize the startup cost for sending a message.
In the receiving side, 
%All-to-all machines data exchange is conducted  so that  
each machine allocates $q$ receive buffers corresponding to
$q$ local partitions, to hold received messages from other machines.  
When a receive buffer for a VM is  full, the data is written to the local disk storage. 
%These substeps are repeated as the stream of data is exchanged when each machine compares through all $q$ partitions.

\item The third step is to read  non-duplicate blocks from each VM and output to the final backup 
storage. Additionally, the global index on each machine is updated with the meta data of new chunk blocks added.
In this process, if a segment is not dirty, we only need to output the segment meta data 
such as reference pointers to the original segments previously saved in the backup.  
If a segment is dirty,  we use the duplicate summary information from Step 2 for internal 
duplicate blocks of this dirty segment and output the remaining non-duplicate blocks to the backup storage.
\end{itemize}

@@

%1) $p$ send buffers. images, sends the fingerprint of a dirty block to a machine that is responsible for this fingerprint.
%2) Buffer requests gathered from other machines and divide those requests into $q$ buckets. Once a buffer for each bucket is full, output to the disk storage.
\item 
For Step 2,  the allocated memory serves 2 purposes. 1) Space for hosting a partition of global index and 
the corresponding partition of  deduplication requests. 2) Buffer space for $q$ receive buffers.
%%accumulating duplicate summary for each targeted VM.   Once  each machine processes a bucket of  duplicate detection requests, 
The duplicate summary sent other machines and acclimated for each VM contains
the block ID and  the reference pointer.   
%For each machine which hosts $v$  VMs, and will receive messages from many other machines, 
%the system needs to allocate buffer space for each VM ot accumulate the duplicate summary records. 
%When a buffer for a VM is full, the result is written to the disk.

\item For Step 3 to  perform the real backup for each VM, 
memory is used to hold the meta information summary of all duplicate blocks obtained  from Step 2. 
Another memory usage is to fetch a sequence of blocks from a virtual machines (most of them are non-duplicate) 
and write them to the  backup storage.

@@

{\bf Snapshot deletion.} Each virtual machine will keep at most $x$ snapshots of VM images and thus
expired snapshots will be deleted unless its owner explicitly asks for its retention. 
A block or the entire segment can be deleted if its reference counter is zero.
%As we discussed in Section~\ref{sect:data}, the reference counter is kept in the global index, partitioned among machines. 
We periodically read all receipts of active 
snapshots and compute the counter of all blocks while still following the fingerprint-based partitioning.
That is based on the idea of mark-and-sweep~\cite{MarkSweep} while 
we deal such snapshot deletion in three partition-based steps similar to the VM snapshot backup.
Step 1 is to read  the meta data of snapshots such as segment and block
recipes and  accumulate  reference count requests in different machines  in the fingerprint based distribution.
The second step  is to count references within each partition and detect those records with zero 
reference. The third step is that every VM gathers the confirmed deletion requests for its content and sends them
to the backup storage.
The archival data repository may log these deletion requests,  and will periodically perform a compaction operation when 
its deletion log is too big. 
%Due to the paper constraint, we will not discuss the deletion operations in details.

### 2013-03-08 hotstorage13/background.tex
ispell

Additional inline deduplications are studied in ~\cite{sparseindex09,idedup}. All of the above appraoches have focused on
such inline duplicate detection, namely given a content chunk block, how to detect if it is duplicate instantantly
to trigger the data backup of this block or not before the detection request for the next blocks can be launched. 
In our work, this constraint is relaxed and 
there is a waiting time for many duplicate detection requests. Our goal is to minimizing  computing  resource without
affeting the overall time of backup.

>>>>

Additional inline deduplication techniques are studied in ~\cite{sparseindex09,idedup}. All of the above approaches have focused on
such inline duplicate detection, namely given a content chunk block, how to detect if it is duplicate instantly
to trigger the data backup of this block or not before the detection request for the next blocks can be launched. 
In our work, this constraint is relaxed and 
there is a waiting time for many duplicate detection requests. Our goal is to minimizing  computing  resource without
affecting the overall time of backup.

### 2013-03-08 hotstorage13/eval.tex
ispell

We have implemented and evaluated a prototype of the parititon-based deduplication scheme on a Linux cluster
of AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  Objectives of our experimental evaluation are:
1) Analyze the processing time and througput of backup for a large cluster of virtual machines.
2) Assess the effectiveness  of partition-based duplication detection 
backup.  3) Examine the impacts of buffering during meta data exchange.

@@

%Since it's impossible to perform large scale analysis without affecting the VM performance,
%We have sampled a data set from 1323 real user VMs from a cluster with 100 nodes 
%to measure the effectiveness of our scheme.
We have performed a trace-driven study using a dataset containing 10 snapsots of 35 VMs.
That is part of a 1323 VM dataset  collected from 100 Aliyun's cloud nodes 
in our earier work with  Alibaba Aliyun~\cite{WeiZhang}.
%In this dataset, there are 10 snapshots per each VM user and the total amount of space 
%investigated is 17.5 terabytes.
%This dataset contas compose of 35 VMs from 7 popular OSes: 
%Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
%5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
%The overall data size for this 700 full snapshots is 17.6 TB.
%This dataset  contains the snapshots of 1323 VMs.
%Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
%study the CDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
All data are divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content blocks ~\cite{similar94,rabin81} with an average size of 4KB.
The signature for variable-sized blocks is computed using their SHA-1 hash. 
%Popularity of data blocks are collected through global counting 
%and the top 1\% will fall into CDS, as discussed in Section~\ref{sect:crossVM}.

@@

Table~\ref{tab:overall} shows the performance of partition-based deduplication when 
the number of partitons per machine ($q$) varies from 50 to 2000.
Row 2 shows the memory usage needed to load a partition of global index and detection requests,
varying from 161MB to 4.025MB. As we impose a constraint of 30MB, then only $q>300$ would be a viable choice.
Row 3 shows the majority of memory usage is for global index.
Row 4 is the total time for a 100-node cluster.
Row 5 is  the throughput per machine reported  is the total 
amount of virtual machine images divided by the processing time. 
The processng time includes the first scanning time
of dirty VM segments to generate block figureprints and the second scan time for real backup.

@@

Table~\ref{tab:memory} shows the performance of partition-based deduplication when 
the memory limit imposed on each node, varying from 
The overall processing time does not have a signficant reduction as we increase memory usage  20MB to 200MB.
As Row 2 shows, the time is mainly dominated by  the IO costs of two scans of VMs.
Thus we conlude that using about 30MB is sufficient to have VM backup completed in parallel within about 3.11 hours.

@@

We have also compared our pre-detection approach with another approach by combining
dirtybit segement  detection and  the data domain method~\cite{Zhu}. 
The bloomer filter setting  results a 1:10 ratio of index reduction for in-memory search before visiting
the disk for the full index with 2\% false positives. The prefetching cache hit ratio is set to be 98.96\% based
a number in ~\cite{Zhu}.
We measure its  total time including one scan of VM dirty segemnts in about 1.38 hours.
That approach takes about 3.19 hours comparable with our pre-detection scheme while its memory cost
includes 1GB of bloom filters and additional space for cache. That is an significant amount of space,
compeuting with other cloud service while memory cost of our setting is  insignifcant.

>>>>

We have implemented and evaluated a prototype of the partition-based deduplication scheme on a Linux cluster
of AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  Objectives of our experimental evaluation are:
1) Analyze the processing time and throughput of backup for a large cluster of virtual machines.
2) Assess the effectiveness  of partition-based duplication detection 
backup.  3) Examine the impacts of buffering during meta data exchange.

@@

%Since it's impossible to perform large scale analysis without affecting the VM performance,
%We have sampled a data set from 1323 real user VMs from a cluster with 100 nodes 
%to measure the effectiveness of our scheme.
We have performed a trace-driven study using a dataset containing 10 snapshots of 35 VMs.
That is part of a 1323 VM dataset  collected from 100 Aliyun's cloud nodes 
in our earlier work with  Alibaba Aliyun~\cite{WeiZhangIEEE}.
%In this dataset, there are 10 snapshots per each VM user and the total amount of space 
%investigated is 17.5 terabytes.
%This dataset contas compose of 35 VMs from 7 popular OSes: 
%Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
%5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
%The overall data size for this 700 full snapshots is 17.6 TB.
%This dataset  contains the snapshots of 1323 VMs.
%Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
%study the CDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.
All data are divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content blocks ~\cite{similar94,rabin81} with an average size of 4KB.
The signature for variable-sized blocks is computed using their SHA-1 hash. 
%Popularity of data blocks are collected through global counting 
%and the top 1\% will fall into CDS, as discussed in Section~\ref{sect:crossVM}.

@@

Table~\ref{tab:overall} shows the performance of partition-based deduplication when 
the number of parititons per machine ($q$) varies from 50 to 2000.
Row 2 shows the memory usage needed to load a partition of global index and detection requests,
varying from 161MB to 4.025MB. As we impose a constraint of 30MB, then only $q>300$ would be a viable choice.
Row 3 shows the majority of memory usage is for global index.
Row 4 is the total time for a 100-node cluster.
Row 5 is  the throughput per machine reported  is the total 
amount of virtual machine images divided by the processing time. 
The processing time includes the first scanning time
of dirty VM segments to generate block fingerprints and the second scan time for real backup.

@@

Table~\ref{tab:memory} shows the performance of partition-based deduplication when 
the memory limit imposed on each node, varying from 
The overall processing time does not have a significant reduction as we increase memory usage  20MB to 200MB.
As Row 2 shows, the time is mainly dominated by  the IO costs of two scans of VMs.
Thus we conclude that using about 30MB is sufficient to have VM backup completed in parallel within about 3.11 hours.

@@

We have also compared our pre-detection approach with another approach by combining
dirtybit segment  detection and  the data domain method~\cite{Zhu}. 
The bloomer filter setting  results a 1:10 ratio of index reduction for in-memory search before visiting
the disk for the full index with 2\% false positives. The prefetching cache hit ratio is set to be 98.96\% based
a number in ~\cite{Zhu}.
We measure its  total time including one scan of VM dirty segments in about 1.38 hours.
That approach takes about 3.19 hours comparable with our pre-detection scheme while its memory cost
includes 1GB of bloom filters and additional space for cache. That is an significant amount of space,
competing with other cloud service while memory cost of our setting is  insignificant.

### 2013-03-08 hotstorage13/intro.tex
ispell

%Virtualization is the engine behind many popular cloud computing platforms.
%Amazon, Alibaba,  and many others have provided public VM clouds that host
%tens of thousands of  virtual machines(VM) created for various active users.
Periodic  archiving of virtual machine (VM) snaps is important 
for long-term data  retention and fault recovery in case of machine failures.  
For example, daily backup of VM images  is conducted automatically 
at Alibaba which provides the largest public cloud service in China.
The cost of frequent backup of VM snapshots is  high because of the huge storage demand.
This issue has been addressed by   storage data deduplication ~\cite{venti02,bottleneck08} that
identifies redundant content duplicates among snapshots.  On the other hand, performing
deduplication adds significant  memory cost for comparison of content fingerprints. 
Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently. 
Cloud providers often wish that the backup service only consumes  the minimal resource usage without 
impacting any existing cloud service.  Another challenge for backup with deduplication is that deletion 
of old snapshot competes computing resource with noticable cost. That is because data dependence created 
by duplicate relationship among snapshots  adds processing complexity, especially when  
VMs can migrate around in the cloud.

@@

%Our solution  only uses a very small amount of memory space during backup while completing  snapshot backup and 
%deletion in a reasonable amount of time. 
The traditional approach to  deduplication for backup is an inline approach which follows
a sequence of VM block reading, duplicate detection,  and nonduplicate  block write to the 
backup storage.  
Our key idea  is to  first perform parallel duplicate pre-detection for VM content blocks 
among all machines before performing actual data backup. Each machine
accumulates detection requests and  then performs pre-detection   parititon by partition 
with minimal resource usage.
Fignureprint based partitioning allows highly parallel duplicate pre-detection  and also simplifies 
reference counting management.  
% as the entire process can also be divided into a
%parition-wise  deletion. 
With careful parallelism management and message buffering during cross-machine data exchange,
this pre-detecton scheme can provide  a sufficient throughput for large-scale cloud data  backup.

>>>>

%Virtualization is the engine behind many popular cloud computing platforms.
%Amazon, Alibaba,  and many others have provided public VM clouds that host
%tens of thousands of  virtual machines(VM) created for various active users.
Periodic  archiving of virtual machine (VM) snaps is important 
for long-term data  retention and fault recovery in case of machine failures.  
For example, daily backup of VM images  is conducted automatically 
at Alibaba which provides the largest public cloud service in China.
The cost of frequent backup of VM snapshots is  high because of the huge storage demand.
This issue has been addressed by   storage data deduplication ~\cite{venti02,bottleneck08} that
identifies redundant content duplicates among snapshots.  On the other hand, performing
deduplication adds significant  memory cost for comparison of content fingerprints. 
Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently. 
Cloud providers often wish that the backup service only consumes  the minimal resource usage without 
impacting any existing cloud service.  Another challenge for backup with deduplication is that deletion 
of old snapshot competes computing resource also. That is because data dependence created 
by duplicate relationship among snapshots  adds processing complexity, especially when  
VMs can migrate around in the cloud.

@@

%Our solution  only uses a very small amount of memory space during backup while completing  snapshot backup and 
%deletion in a reasonable amount of time. 
The traditional approach to  deduplication for backup is an inline approach which follows
a sequence of VM block reading, duplicate detection,  and non-duplicate  block write to the 
backup storage.  
Our key idea  is to  first perform parallel duplicate pre-detection for VM content blocks 
among all machines before performing actual data backup. Each machine
accumulates detection requests and  then performs pre-detection   partition by partition 
with minimal resource usage.
Fingerprint based partitioning allows highly parallel duplicate pre-detection  and also simplifies 
reference counting management.  
% as the entire process can also be divided into a
%parition-wise  deletion. 
With careful parallelism management and message buffering during cross-machine data exchange,
this pre-detection scheme can provide  a sufficient throughput for backup.

### 2013-03-08 hotstorage13/main.tex
5 papges
ispell

\begin{document}
%\title{Selective Deduplication for VM Snapshots in Cloud Storage}
\title{ Low-Cost Data Deduplication  for  Virtual Machine Backup in Cloud Storage}
%\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
\author{
Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$\\
   {\normalsize $^\star$UC Santa Barbara, \{wei, tyang\}@cs.ucsb.edu}
}

@@

%  }%
%  {%
%    \end{oldthebibliography}%
%  }
{
\bibliographystyle{abbrv}
\bibliography{library,dedup1}
}
\end{document}

>>>>

\begin{document}
%\title{Selective Deduplication for VM Snapshots in Cloud Storage}
\title{ Low-Cost Data Deduplication  for  Virtual Machine Backup in Cloud Storage}
%\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}

\author{
Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, Hong Tang$^\dagger$ \\
{\normalsize$^\star$Department of Computer Science, University of California at Santa Barbara}
  {\normalsize$^\dagger$Alibaba Inc.}
}

% \{wei, tyang\}@cs.ucsb.edu

@@

%  }%
%  {%
%    \end{oldthebibliography}%
%  }
{\small
\bibliographystyle{abbrv}
\bibliography{library,dedup1}
}
\end{document}
